Estimating Output Loss due to being Unrecognized as States

### 2019-03-07 paper/paper.tex
Discuss the results on predicted economic growth #41

Table \ref{country_fe_results} reports the results from estimating equation (\ref{country_fe}). 
The country fixed effects estimated from equation (\ref{gdp})) are proportional to the average light intensity. 
Figure \ref{country_fe_graph} plots the country fixed effects against the average light intensity.

Plugging the coefficient estimates in Tables \ref{panel_results} and \ref{country_fe_results} as well as annual nighttime light observations into equation (\ref{prediction}) yields the predicted real GDP for unrecognized states and their parent countries. 
We plot these predicted values over time in Figure \ref{predicted_gdp}. 
As a validation exercise, we also plot the observed annual real GDP for the respective parent country, obtained from the Penn World Table.

@@

>>>>

Plugging the coefficient estimates in Table \ref{panel_results} together with annual nighttime light observations into equation (\ref{growth}) yields the predicted growth of real GDP for unrecognized states and their parent countries. 
Figures \ref{aze} to \ref{tra} plot these predictions.

\subsection{Validation}
We first validate our methodology by comparing the predicted growth with the actual growth of real GDP from the Penn World Table for the three parent countries. 
% Azerbaijan
Figure \ref{aze} shows the results for Azerbaijan.
For years 1993-2004 and 2012-2013, the predicted growth rates do not align well with the actual growth rates, even showing a wrong sign in some years. 
From 2005 to 2011, however, the predicted growth rates capture the trend in the actual growth rates. 
The predicted growth generally underestimates the actual growth, probably because nighttime light does not capture the GDP growth due to oil exports.
% Georgia
Figure \ref{geo} compares the actual growth rates with the predicted ones for Georgia. 
Similarly to Azerbaijan, years 1993-2003 see discrepancies between the predicted and actual growth rates, with opposite signs in some years. 
For years 2004-2013, however, the predicted growth roughly picks up the trend in the actual growth, with the magnitude also comparable.
% Moldova
Figure \ref{mda} shows the results for Moldova.
For years 1993-2003 and 2011-2013, the predicted growth deviates from the actual growth, with a wrong sign in some years.
Years 2004-2010 see the predicted growth approximate the actual growth relatively well.
% Summary
Overall, the predicted growth around years 2004-2010 is trustworthy. Outside this period, either our prediction methodology fails or the official GDP statistics from these countries is prone to errors.

\subsection{Predicted Growth in Unrecognized States}
We now compare the predicted annual growth rates between unrecognized states and their parent countries. 
We use as a benchmark the predicted growth, not the actual growth, in the parent countries because the underlying data generating process is comparable.

\paragraph{Nagorno-Karabakh}
Figure \ref{nkr} shows the predicted annual real GDP growth rates for Nagorno-Karabakh in comparison to the predicted growth for its parent country, Azerbaijan. 
For years 1993-1995, Karabakh's economy is estimated to have shrunk by over 10\% annually, reflecting the damage from the war of secession from Azerbaijan. 
From 1996 to 2004, the estimated economic growth was very volatile.
For the period 2005-2011, where Azerbaijan's predicted growth rates trace the trend in the actual growth, Nagorno-Karabakh's economic growth exceeds 10\% (except for 2009 and 2011). 
These growth rates exceed the predicted growth rates in Azerbaijan proper.
It may just reflect the higher marginal product of capital per worker in Nagorno-Karabakh as the territory is poorer than the rest of Azerbaijan. 
However, it may also suggest that the impact of being unrecognized as a sovereign state is minimal in terms of economic recovery from civil wars in the case of Nagorno-Karabakh.

\paragraph{Abkhazia}
Figure \ref{abk} shows the predicted annual real GDP growth for Abkhazia in comparison to the predicted growth in Georgia proper. 
For years 1993-2003, the estimated economic growth rates are very volatile in Abkhazia though the ones in Georgia are equally volatile as well.
For the period 2004-2013, when Georgia's predicted growth corresponds well with its actual growth, Abkhazia's growth rates are positive and largely comparable to Georgia's growth.   
Overall, the impact of being unrecognized as a sovereign state appears to be minimal in the case of Abkhazia as long as Georgia proper is a valid counterfactual.

\paragraph{South Ossetia}
Figure \ref{sos} compares the predicted growth rates for South Ossetia with the ones for Georgia proper.
For the period 2004-2013, when Georgia's predicted and actual growth rates co-move, South Ossetia's predicted growth is comparable to Georgia's.
From 2010, South Ossetia outperforms Georgia in predicted growth, probably reflecting the consequences of South Ossetian War in 2008: Russia actively helps South Ossetia financially while Georgia loses its trade with Russia.

\paragraph{Transnistria}
Finally, Figure \ref{tra} reports the predicted economic growth rates for Transnistria in comparison to those for Moldova proper. 
Transnistria's predicted economic growth is volatile during the entire sample period, including years 2004-2010, when Moldova's predicted and actual real GDP growth rates correspond well to each other. 
Its magnitude is overall smaller than the other three unrecognized states.
The same remarks apply to its parent country, Moldova, suggesting that the impact of being unrecognized as a sovereign state is minimal in the case of Transnistria.

@@

\begin{figure}[ptb]
\caption{Actual and Predicted Annual Real GDP Growth in Azerbaijan}%
\label{aze}%
\includegraphics[width=\linewidth]{../a_output/plot_growth_hat_AZE.png}
{\scriptsize \textit{Notes}: 
	The data source for the actual annual real GDP growth is the Penn World Table (version 9.0). 
	The predicted annual real GDP growth is based on nighttime light intensity within Azerbaijan proper, excluding the territory occupied by Nagorno-Karabakh's authority. 
}
\end{figure}

\begin{figure}[ptb]
\caption{Actual and Predicted Annual Real GDP Growth in Georgia}%
\label{geo}%
\includegraphics[width=\linewidth]{../a_output/plot_growth_hat_GEO.png}
{\scriptsize \textit{Notes}: 
	The data source for the actual annual real GDP growth is the Penn World Table (version 9.0). 
	The predicted annual real GDP growth is based on nighttime light intensity within Georgia proper, excluding the Soviet-era territories of Abkhazia and South Ossetia. 
}
\end{figure}

\begin{figure}[ptb]
\caption{Actual and Predicted Annual Real GDP Growth in Moldova}%
\label{mda}%
\includegraphics[width=\linewidth]{../a_output/plot_growth_hat_MDA.png}
{\scriptsize \textit{Notes}: 
	The data source for the actual annual real GDP growth is the Penn World Table (version 9.0). 
	The predicted annual real GDP growth is based on nighttime light intensity within Moldova proper, excluding the Soviet-era territory of Transnistria. 
	The actual growth in 1993 is very close to zero, rather than being missing in the data source.
}
\end{figure}

\begin{figure}[ptb]
\caption{Predicted Annual Real GDP Growth in Nagorno-Karabakh and Azerbaijan}%
\label{nkr}%
\includegraphics[width=\linewidth]{../a_output/plot_growth_hat_NKR.png}
{\scriptsize \textit{Notes}: 
	The predicted annual real GDP growth for Nagorno-Karabakh is due to the author's calculation (see the text for detail).
	The corresponding data for Azerbaijan is the same as in Figure \ref{aze}.
}
\end{figure}

\begin{figure}[ptb]
\caption{Predicted Annual Real GDP Growth in Abkhazia and Georgia}%
\label{abk}%
\includegraphics[width=\linewidth]{../a_output/plot_growth_hat_ABK.png}
{\scriptsize \textit{Notes}: 
	The predicted annual real GDP growth for Abkhazia is due to the author's calculation (see the text for detail).
	The corresponding data for Georgia is the same as in Figure \ref{geo}.
}
\end{figure}

\begin{figure}[ptb]
\caption{Predicted Annual Real GDP Growth in South Ossetia and Georgia}%
\label{sos}%
\includegraphics[width=\linewidth]{../a_output/plot_growth_hat_SOS.png}
{\scriptsize \textit{Notes}: 
	The predicted annual real GDP growth for South Ossetia is due to the author's calculation (see the text for detail).
	The corresponding data for Georgia is the same as in Figure \ref{geo}.
}
\end{figure}

\begin{figure}[ptb]
\caption{Predicted Annual Real GDP Growth in Transnistria and Moldova}%
\label{tra}%
\includegraphics[width=\linewidth]{../a_output/plot_growth_hat_TRA.png}
{\scriptsize \textit{Notes}: 
	The predicted annual real GDP growth for Transnistria is due to the author's calculation (see the text for detail).
	The corresponding data for Moldova is the same as in Figure \ref{mda}.
}
\end{figure}
